\GVN{}-Hoist: Hoisting Computations from Branches

### 2016-08-26 hoist.tex
abstract

\maketitle
\begin{abstract}
  Code-hoisting identifies identical computations across the program and hoists
  them to a common dominator so as to save code size.  Although the main goal of
  code-hoisting is not to remove redundancies: it effectively exposes
  redundancies and enables other passes like LICM to remove more redundancies.
  The main goal of code-hoisting is to reduce code size with the added benefit
  of exposing more instruction level parallelism and reduced register pressure.

  We present a code hoisting pass that we implemented in \LLVM{}. It is based on
  Global Value Numbering infrastructure available in \LLVM{}. The experimental
  results show an average of 2.5\% savings in code size, although the code size
  increases in many cases because it enables more inlining. This is an
  optimistic algorithm in the sense that we consider all identical computations
  in a function as potential candidates to be hoisted. We make an extra effort
  to hoist candidates by partitioning the potential candidates in a way to
  enable partial hoisting in case common hoisting points for all the candidates
  cannot be found. We also formalize cases when register pressure will reduce as
  a result of hoisting.
\end{abstract}

@@

However, in the special case discussed in Section~\ref{hoist:reg-pressure}, it
will be okay to hoist because the register pressure would not decrease.

>>>>

\maketitle
\begin{abstract}
  Code-hoisting identifies identical computations across the program and hoists
  them to a common dominator so as to save code size.  Not only code-hoisting
  saves code size, a) It exposes redundancies in some cases, b) It exposes more
  instruction level parallelism in the basic block a computation is hoisted, and
  c) It enables other passes like LICM to remove more redundancies.

  We present a code hoisting pass that we implemented in \LLVM{}. It is based on
  Global Value Numbering infrastructure available in \LLVM{}. The experimental
  results show an average of 2.5\% savings in code size, although the code size
  also increases in many cases because it enables more inlining. This is an
  optimistic algorithm in the sense that it considers all identical computations
  in a function as potential candidates to be hoisted. We make an extra effort
  to hoist candidates by partitioning the potential candidates in a way to
  enable partial hoisting in case common hoisting points for all the candidates
  cannot be found. We also formalize cases when register pressure will reduce as
  a result of hoisting and why sorting the list of potential candidates
  w.r.t. their DFS numbers helps hoist more candidates with less compile time
  overhead.
\end{abstract}

@@

However, in the special case discussed in Section~\ref{hoist:reg-pressure}, it
will be okay to hoist because the register pressure would not increase.
